---
title: "Anime Box Plots"
author: "Kyle MacDonald"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, message = F, warning = F)
```

```{r libraries, include=FALSE}
# load helper functions and set theme
source(here("R/helper_functions/", "libraries_v_3.3.R"))
library(magrittr); library(kmr); library(cowplot); library(here)
library(rogme); library(ggridges)
library(tidyverse)
theme_set(ggthemes::theme_few())
```

## Read data

```{r}
d <- read_csv(here("data/03_summary_tables", "anime_participant_level.csv"))
d_models <- readRDS(here("data/03_summary_tables", "anime-posterior-samples.rds"))
d_trial_level <- read_csv(here("data/03_summary_tables", "anime_trial_level.csv"))
```

## Experiment 1

```{r}
samples_e1_acc <- d_models$acc_e1 %>% 
  mutate(condition = str_c(cue_type, trial_type, sep = "_")) 
```

Compute summaries of posterior distributions over accuracy estimates.

```{r}
ms_acc_e1 <- samples_e1_acc %>% 
  filter(condition != "onomatopoeic_novel") %>% 
  group_by(cue_type, trial_type) %>% 
  summarise(m = mean(acc_prob_scale),
            hdi_lower = quantile(acc_prob_scale, probs = 0.05),
            hdi_upper = quantile(acc_prob_scale, probs = 0.95)) %>% 
  mutate_if(.predicate = is.numeric, .funs = round, digits = 2) 
```

Make the data and group means model plot

```{r}
p <- d %>% 
  filter(experiment == "e1") %>% 
  mutate(trial_type = fct_relevel(trial_type, "disambiguation", after = 1), 
         trial_type = recode(trial_type, disambiguation = "novel")) %>% 
  ggplot(aes(x = cue_type, y = ss_prop_looking)) +
  ggbeeswarm::geom_quasirandom(shape = 21, width = 0.15, color = "black", 
                               fill = "darkgrey",
                               alpha = 0.3,
                               size = 3) + 
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  facet_wrap(~trial_type, scales = "free_x", ncol = 1) +
  labs(x = "Cue Type", y = "Prop. Target Looking") +
  lims(y = c(0, 1)) 

# get model values
d_model_vals <- samples_e1_acc %>% 
  filter(condition != "onomatopoeic_novel") %>% 
  dplyr::rename(ss_prop_looking = acc_prob_scale) %>% 
  mutate(cue_type = ifelse(cue_type == "onomatopoeia", "onomatopoeic", cue_type))

# get quantile vals
d_quantiles <- d_model_vals %>% 
  group_by(cue_type, trial_type) %>% 
  summarise(ci_lower = hd(ss_prop_looking, q = 0.025),
            ci_upper = hd(ss_prop_looking, q = 0.975),
            ss_prop_looking = hd(ss_prop_looking, q = 0.5))

p <- p + 
  geom_pointrange(aes(ymax = ci_upper, ymin = ci_lower), 
                  data = d_quantiles,
                  color = "grey20",
                  shape = 15,
                  size = 0.7)
p
```

Clean up the posterior samples to make the plot.

```{r}
e1_acc_hyp_d <- samples_e1_acc %>% 
  filter(condition != "onomatopoeic_novel") %>% 
  select(-param_estimate, -condition) %>% 
  spread(key = cue_type, value = acc_prob_scale) %>% 
  mutate(name_onomatopoeic_diff = name - onomatopoeic,
         name_vocalization_diff = name - vocalization,
         onomatopeic_vocalization_diff = onomatopoeic - vocalization) %>% 
  select(-name, -onomatopoeic, -vocalization) %>% 
  gather(key = ind_contrast, value = param_est, -sample_id, - trial_type) %>% 
  filter(!is.na(param_est))
```

Make the group differences plot.

```{r}
e1_acc_group_diff_plot <- e1_acc_hyp_d %>% 
  mutate(param_est = param_est * -1, 
         ind_contrast = recode(ind_contrast, 
                               name_onomatopoeic_diff = "name_onomatopeia",
                               name_vocalization_diff = "name_vocalization",
                               onomatopeic_vocalization_diff = "onomatopeia_vocalization"),
         ind_contrast_fact = factor(ind_contrast)) %>% 
  ggplot(aes(x = param_est, y = fct_reorder(ind_contrast, param_est), 
             fill = ind_contrast_fact)) + 
  geom_density_ridges(scale = 1.5, alpha = 0.8, rel_min_height = 0.005) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "black", size = 1) +
  guides(fill = F) +
  scale_y_discrete(expand = c(0.2, 0)) +
  scale_fill_grey() +
  lims(x = c(-0.15, 0.2)) + 
  labs(x = "Difference in Accuracy", 
       y = NULL) +
  facet_wrap(~trial_type, scales = "free_y", ncol = 1) 

e1_acc_group_diff_plot
```

Build the final plot

```{r}
e1_acc_final_plot <- plot_grid(p, e1_acc_group_diff_plot, 
                               scale = c(0.95, 0.85),
                               rel_widths = c(1, 1.2), 
                               labels = c("a", "b"))
e1_acc_final_plot
```

```{r}
save_plot(e1_acc_final_plot, 
          filename = here("paper/figs", "prop_look_e1_new.png"), 
          ncol = 2.2,
          nrow = 1.4,
          base_aspect_ratio = 1)
```

## Experiment 2

```{r}
samples_e2_acc <- d_models$acc_e2 
```

```{r}
ms_acc_e2 <- samples_e2_acc %>% 
  group_by(trial_type) %>% 
  summarise(m = mean(acc_prob_scale),
            hdi_lower = quantile(acc_prob_scale, probs = 0.05),
            hdi_upper = quantile(acc_prob_scale, probs = 0.95)) %>% 
  mutate_if(.predicate = is.numeric, .funs = round, digits = 4) 
```

```{r}
p_e2 <- d %>% 
  filter(experiment == "e2") %>% 
  mutate(trial_type = fct_relevel(trial_type, "disambiguation", after = 1)) %>% 
  ggplot(aes(x = trial_type, y = ss_prop_looking)) +
  ggbeeswarm::geom_quasirandom(shape = 21, width = 0.15, color = "black", 
                               fill = "darkgrey",
                               alpha = 0.3,
                               size = 3) + 
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  labs(x = "Trial Type", y = "Prop. Target Looking") +
  lims(y = c(0, 1)) 

# get model values
d_model_vals_e2 <- samples_e2_acc %>% 
  dplyr::rename(ss_prop_looking = acc_prob_scale) 

# get quantile vals
d_quantiles <- d_model_vals_e2 %>% 
  group_by(trial_type) %>% 
  summarise(ci_lower = hd(ss_prop_looking, q = 0.025),
            ci_upper = hd(ss_prop_looking, q = 0.975),
            ss_prop_looking = hd(ss_prop_looking, q = 0.5))

p_e2 <- p_e2 + 
  geom_pointrange(aes(ymax = ci_upper, ymin = ci_lower), 
                  data = d_quantiles,
                  color = "grey20",
                  shape = 15,
                  size = 0.7)

p_e2
```

Clean up the posterior samples to make the plot.

```{r}
e2_acc_hyp_d <- samples_e2_acc %>% 
  select(-param_estimate) %>% 
  spread(key = trial_type, value = acc_prob_scale) %>% 
  mutate(familiar_disambiguation = familiar - disambiguation,
         familiar_retention = familiar - retention,
         disambiguation_retention = disambiguation - retention) %>% 
  select(-disambiguation, -familiar, -retention) %>% 
  gather(key = ind_contrast, value = param_est, -sample_id) %>% 
  filter(!is.na(param_est))
```

Make the group differences plot.

```{r}
e2_acc_group_diff_plot <- e2_acc_hyp_d %>% 
  mutate(ind_contrast_fact = factor(ind_contrast)) %>% 
  ggplot(aes(x = param_est, y = fct_reorder(ind_contrast, param_est), 
             fill = ind_contrast_fact)) + 
  geom_density_ridges(scale = 1.5, alpha = 0.8, rel_min_height = 0.005) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "black", size = 1) +
  guides(fill = F) +
  scale_y_discrete(expand = c(0.2, 0)) +
  scale_fill_grey() +
  labs(x = "Difference in Accuracy", 
       y = NULL) 

e2_acc_group_diff_plot
```

Build the final plot for experiment 2. 

```{r}
e2_acc_final_plot <- plot_grid(p_e2, e2_acc_group_diff_plot, 
                               rel_widths = c(1, 1.2), 
                               scale = c(0.95, 0.9),
                               labels = c("a", "b"))
e2_acc_final_plot
```

```{r}
save_plot(e2_acc_final_plot, 
          filename = here("paper/figs", "prop_look_e2_new.png"),
          ncol = 2.2,
          nrow = 1,
          base_aspect_ratio = 1)
```
