---
title: "Anime data summarizing"
author: "Kyle MacDonald"
date: "October 12, 2016"
output: html_document
---

```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F)
```

```{r libraries, include=FALSE}
library(tidyverse); library(lme4); library(langcog);
library(devtools); library(lwl); library(magrittr)
library(kmr); library(knitr)
```

This script takes the tidy eye movement data from the Anime project and converts it to a summary data file. 

```{r read data}
ichart.df <- read_csv("data/tidy_data/anime_tidy_ichart.csv")
cdi.df <- read_csv("data/tidy_data/anime_tidy_cdi.csv")
```

## Filters

Get number of prescreened out trials for each participant and compute how many trials are left for each after prescreening.

```{r number of good trials}
ss_trials <- ichart.df %>% 
  select(Sub.Num, Prescreen.Notes, Tr.Num) %>% 
  unique() %>% 
  group_by(Sub.Num) %>% 
  dplyr::summarise(num_trials_before_ps = n())

ss_trials <- ichart.df %>% 
  select(Sub.Num, Prescreen.Notes, Tr.Num) %>% 
  unique() %>% 
  group_by(Sub.Num) %>% 
  filter(Prescreen.Notes != "") %>% 
  dplyr::summarise(num_prescreened = n()) %>% 
  left_join(., ss_trials, by = "Sub.Num") %>% 
  mutate(num_trials_final = num_trials_before_ps - num_prescreened)
```

Filter out prescreened trials.

```{r filter prescreened}
ichart.df %<>% filter(is.na(Prescreen.Notes) == TRUE)
```

### Compute proportion looking to Target, Distractor, and Away 

```{r}
ichart.df %>% 
  select(Sub.Num, Tr.Num, Response) %>% 
  unique() %>% 
  group_by(Response) %>% 
  summarise(n_trials = n()) %>% 
  kable()
```


```{r get count at each time slice}
includeAways <- FALSE ## Controls whether you want AWAYS included in computation

if (includeAways) { 
  include_vals <- c("0", "1", ".")
} else {
  include_vals <- c("0", "1")
}

ms.ichart <- ichart.df %>% 
  filter(value %in% include_vals) %>%  
  group_by(Sub.Num, Time.ms, Condition, experiment, value_cat) %>% 
  dplyr::summarise(count = ifelse(n() == 0, 0, n())) %>% 
  dplyr::summarise(sum_count = sum(count)) %>% 
  ungroup() %>% 
  mutate(Sub.Num = as.character(Sub.Num))
```

```{r get prop looking at each timeslice}
ms.ichart <- as.data.frame(xtabs(~ Sub.Num + value_cat + Time.ms + Condition + experiment, 
                                    data = filter(ichart.df, 
                                                  value %in% include_vals)),
                           stringsAsFactors = F) %>% 
  mutate(Time.ms = to.n(Time.ms)) %>% 
  left_join(x = ms.ichart, by = c("Sub.Num", "Time.ms", "Condition", "experiment")) %>% 
  mutate(proportion_looking = Freq / sum_count)
```

### Compute graph values for proportion looking at each 33ms timeslice

```{r}
ms_mean_iChart <- ms.ichart %>% 
  filter(to.n(Time.ms) >= 300, to.n(Time.ms) <= 4000) %>% 
  group_by(Time.ms, Condition, value_cat, experiment) %>% 
  multi_boot_standard(column = "proportion_looking", na.rm = T)
```

Write graph values to CSV.

```{r write graph values}
write_csv(x = ms_mean_iChart, path = "data/summary_tables/anime_gvals.csv")
```

### Compute mean proportion looking to target and distractor for each participant and for each participant

This collapses across the entire analysis window

```{r compute mean looking}
ss.cond.mean.looking <- ms.ichart %>% 
  filter(to.n(Time.ms) >= 300, to.n(Time.ms) <= 4000) %>% 
  group_by(Sub.Num, value_cat, Condition) %>% 
  summarise(ss_prop_looking = mean(proportion_looking, na.rm = T)) 
```

Merge participant looking behavior with CDI and demographic information.

```{r merge looking and cdi scores}
ss.summary.final <- cdi.df %>% 
  mutate(Sub.Num = as.character(Sub.Num)) %>% 
  left_join(x = ss.cond.mean.looking, y = ., by = "Sub.Num")
```

Write participant-level summary table to CSV.

```{r write ss summary table}
write_csv(x = ms_mean_iChart, path = "data/summary_tables/anime_ss_summary.csv")
```
