---
title: "Anime data summarizing"
author: "Kyle MacDonald"
output: html_document
---

```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F)
```

```{r libraries, include=FALSE}
library(devtools); library(lwl); library(magrittr)
library(kmr); library(knitr)
library(tidyverse);
```

```{r}
read_path <- "../../data/02_tidy_data/"
write_path <- "../../data/03_summary_tables/"
```

This script takes the tidy eye movement data from the Anime project and converts it to several summary data files: 

  * graph values: proportion looking for each 33ms time slice
  * participant-level: proportion looking for each participant for each trial

```{r read data}
ichart.df <- read_csv(paste0(read_path, "anime_tidy_ichart.csv"))
ichart.df %<>% mutate(Sub.Num = as.character(Sub.Num),
                      Tr.Num = as.character(Tr.Num))

cdi.df <- read_csv(paste0(read_path, "anime_tidy_cdi.csv"))
cdi.df %<>% mutate(Sub.Num = as.character(Sub.Num))
```

### Compute proportion looking to Target, Distractor, and Away 

What's the distribution of looking at critical onset of the auditory stimulus?

```{r}
ichart.df %>% 
  select(Sub.Num, Tr.Num, Response) %>% 
  unique() %>% 
  group_by(Response) %>% 
  summarise(n_trials = n()) %>% 
  kable()
```

get count at each time slice

```{r}
includeAways <- FALSE ## Controls whether you want AWAYS included in computation

if (includeAways) { 
  include_vals <- c("0", "1", ".")
} else {
  include_vals <- c("0", "1")
}

graph_values <- ichart.df %>% 
  filter(value %in% include_vals) %>%  
  group_by(Time.ms, cue_type, trial_type, experiment, value_cat) %>% 
  dplyr::summarise(count = ifelse(n() == 0, 0, n())) %>% 
  dplyr::summarise(sum_count = sum(count))
```

Get prop looking at each timeslice

```{r}
graph_values <- as.data.frame(xtabs(~ value_cat + Time.ms + cue_type + trial_type + experiment, 
                                    data = filter(ichart.df, value %in% include_vals)),
                           stringsAsFactors = F) %>% 
  mutate(Time.ms = to.n(Time.ms)) %>% 
  left_join(x = graph_values, by = c("Time.ms", 
                                  "cue_type", "trial_type", 
                                  "experiment")) 
```

### Compute graph values for proportion looking at each 33ms timeslice

```{r}
graph_values %<>% 
  mutate(prop_looking = Freq / sum_count) %>% 
  group_by(Time.ms, cue_type, trial_type, value_cat, experiment) %>% 
  summarise(m_prop_looking = mean(prop_looking, na.rm = T)) 
```

Write graph values to CSV (note that these are collapsing across participants and trials).

```{r write graph values}
write_csv(x = graph_values, path = paste0(write_path, "anime_gvals.csv"))
```

### Compute prop looking and RT at trial-level

```{r}
rts <- ichart.df %>% 
  select(Sub.Num, Tr.Num, RT, Response, trial_type, cue_type, target_img_type, 
         distracter_img_type, clean_target_img, GoodFirstGap, GoodRT, GoodLongestGap, 
         experiment) %>% 
  unique()
```

Note the key difference in this computation is that we are collapsing proportion looking over the analysis window, so we remove Time.ms from the xtabs function.

```{r}
includeAways <- F ## Controls whether you want AWAYS included in computation

if (includeAways) { 
  include_vals <- c("0", "1", ".")
} else {
  include_vals <- c("0", "1")
}

window_lower <- 0
window_upper <- 3000
```


```{r}
trial_level_summary <- ichart.df %>% 
  filter(value %in% include_vals,
         Time.ms_numeric >= window_lower, Time.ms_numeric <= window_upper) %>%  
  group_by(Sub.Num, Tr.Num, cue_type, trial_type, experiment, value_cat) %>% 
  dplyr::summarise(count = ifelse(n() == 0, 0, n())) %>% 
  dplyr::summarise(sum_count = sum(count)) %>% 
  ungroup() %>% 
  mutate(Sub.Num = as.character(Sub.Num),
         Tr.Num = as.character(Tr.Num))

trial_level_summary <- as.data.frame(xtabs(~ Sub.Num + Tr.Num + value_cat  + cue_type + 
                                   trial_type + experiment, 
                                    data = filter(ichart.df, value %in% include_vals,
                                                  Time.ms_numeric >= window_lower, 
                                                  Time.ms_numeric <= window_upper)),
                           stringsAsFactors = F) %>% 
  left_join(x = trial_level_summary, by = c("Sub.Num", "Tr.Num", 
                                  "cue_type", "trial_type", 
                                  "experiment")) %>% 
  mutate(proportion_looking = Freq / sum_count)
```

Next we get the mean accuracy for each trial.

```{r}
trial_level_summary %<>% 
  group_by(Sub.Num, Tr.Num, cue_type, trial_type, value_cat, experiment) %>% 
  summarise(m_prop_looking = mean(proportion_looking, na.rm = T)) %>% 
  left_join(., rts, by = c("Sub.Num", "Tr.Num", "experiment", "trial_type", "cue_type")) %>% 
  filter(value_cat == "Target") %>% 
  ungroup() %>% 
  select(-value_cat) %>% 
  mutate(Tr.Num = as.integer(Tr.Num))
```

Merge participant looking behavior with CDI and demographic information.

```{r merge looking and cdi scores}
trial_summary_final <- cdi.df %>% 
  left_join(x = trial_level_summary, y = ., 
            by = c("Sub.Num", "experiment"))
```

Write trial-level data to CSV.

```{r}
write_csv(trial_summary_final, path = paste0(write_path, "anime_trial_level.csv"))
```

### Compute mean prop looking at participant-level

This collapses across the entire analysis window and gives you a target looking score for each trial for each participant.

```{r compute mean looking}
ss.cond.mean.looking <- trial_summary_final %>% 
  group_by(Sub.Num, cue_type, trial_type, experiment) %>% 
  summarise(ss_prop_looking = mean(m_prop_looking, na.rm = T)) 
```

Merge participant looking behavior with CDI and demographic information.

```{r merge looking and cdi scores}
ss.summary.final <- cdi.df %>% 
  left_join(x = ss.cond.mean.looking, y = ., by = c("Sub.Num", "experiment"))
```

Write participant-level summary table to CSV.

```{r write ss summary table}
write_csv(x = ss.summary.final, path = paste0(write_path, "anime_participant_level.csv"))
```

## Compute graph values for OC plot

We do the same computations but only for trials where participants started looking at the distracter image at the onset of the auditory cue. 

```{r}
includeAways <- FALSE ## Controls whether you want AWAYS included in computation

if (includeAways) { 
  include_vals <- c("0", "1", ".")
} else {
  include_vals <- c("0", "1")
}

ms_ichart_oc <- ichart.df %>% 
  filter(value %in% include_vals, 
         Response == "D") %>%  
  group_by(Sub.Num, Tr.Num, Time.ms, cue_type, trial_type, experiment, value_cat) %>% 
  dplyr::summarise(count = ifelse(n() == 0, 0, n())) %>% 
  dplyr::summarise(sum_count = sum(count)) %>% 
  ungroup() %>% 
  mutate(Sub.Num = as.character(Sub.Num),
         Tr.Num = as.character(Tr.Num))
```

```{r}
ms_ichart_oc <- as.data.frame(xtabs(~ Sub.Num + Tr.Num + value_cat + Time.ms + cue_type + 
                                   trial_type + experiment, 
                                    data = filter(ichart.df, value %in% include_vals)),
                           stringsAsFactors = F) %>% 
  mutate(Time.ms = to.n(Time.ms)) %>% 
  left_join(x = ms_ichart_oc, by = c("Sub.Num", "Tr.Num", "Time.ms", 
                                  "cue_type", "trial_type", 
                                  "experiment")) %>% 
  mutate(proportion_looking = Freq / sum_count)
```

### Compute graph values for proportion looking at each 33ms timeslice

```{r}
ss_ichart_oc <- ms_ichart_oc %>% 
  group_by(Sub.Num, Time.ms, cue_type, trial_type, value_cat, experiment) %>% 
  summarise(m_prop_looking = mean(proportion_looking, na.rm = T)) 

ms_ichart_oc <- ss_ichart_oc %>% 
  filter(value_cat == "Target", Time.ms <= 1500) %>% 
  group_by(Time.ms, cue_type, trial_type, experiment) %>% 
  langcog::multi_boot_standard(column = "m_prop_looking", na.rm = T, nboot = 500)

beepr::beep(sound = "fanfare")
```

Save graph values for visualization.

```{r write graph values oc}
write_csv(x = ms_ichart_oc, path = paste0(write_path, "anime_gvals_oc_plot.csv"))
```