---
title: "Anime data munge"
author: "Kyle MacDonald"
date: "October 12, 2016"
output: html_document
---

```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F)
```

```{r libraries, include=FALSE}
source("../helper_functions/libraries_v_3.3.R")
library(langcog);library(lwl); library(magrittr); library(kmr)
library(tidyverse)
```

This script takes raw data files from the Anime project and converts them to tidy data files for analysis and visualization. The raw data is in the form of .csv files, which contain vocabulary measures (mCDI) and eye movement data (looking-while-listening task). The tidy data is two files: 

  * a summary table with a vocab score and a mean looking behavior score for each participant
  * a table with graph values for the visualization of looking behavior over time in the task

## Read data

We have two cdi files: one for each experiment.

```{r read cdi}
anime_cdi <- read_csv("../../data/01_raw_data/AniME.newCDI.csv") %>% 
  select(ParticipantId, Gender, CDIAge, VOCAB, ANIMALS, SOUND) %>% 
  mutate(experiment = "e2")

animoo_cdi <- read_csv("../../data/01_raw_data/AniMoo.CDI.new.csv") %>% 
  select(ParticipantId, Gender, CDIAge, VOCAB, ANIMALS, SOUND) %>% 
  mutate(experiment = "e1")
```

We have three iCharts: Anime A, Anime B, Anime Retention

```{r read iCharts}
anime.a.ichart <- readiChart("../../data/01_raw_data/ANIME_A_iChart.txt") 
anime.b.ichart <- readiChart("../../data/01_raw_data/ANIME_B_iChart.txt")
anime.c.ichart <- readiChart("../../data/01_raw_data/ANIME_retention_iChart.txt")
```

## Data cleaning 

Clean up the condition names.

```{r clean condition names}
# anime_a (names and lexicalized animal sound trials)
anime.a.ichart$Condition <- gsub(anime.a.ichart$Condition, 
                                 pattern = "P", 
                                 replacement =  "") 

anime.a.ichart$Condition <- recode(anime.a.ichart$Condition, 
         vanilla = "name_fam_fam_familiar", sounds = "onomatopoeic_fam_fam_familiar",
         NF = "name_nov_fam_disambiguation", FN = "name_fam_nov_familiar")

# anime_b (vocalization trials)
anime.b.ichart$Condition <- recode(anime.b.ichart$Condition, 
         FF = "vocalization_fam_fam_familiar", FN = "vocalization_fam_nov_familiar",
         NF = "vocalization_nov_fam_disambiguation")

# anime_c (retention of names and animal sounds)
anime.c.ichart$Condition <- recode(anime.c.ichart$Condition, 
         FF = "vocalization_fam_fam_familiar", FN = "vocalization_fam_nov_familiar",
         NF = "vocalization_nov_fam_disambiguation", NT = "vocalization_nov_nov_retention")
```

Remove weird "E" condition from anime.c dataframe.

```{r}
anime.c.ichart %<>% filter(Condition != "E")
```

Add variable to track experiment (experiment 2 has retention trials). To make merging easier, we select the same number of columns -- 0-6000ms -- for each experiment. 

```{r track experiment}
anime.a.ichart %<>% 
  mutate(experiment = "e1") %>%
  select(Sub.Num, Tr.Num, Months, Prescreen.Notes, Target.Image,
         Condition, Response, RT, `0`:`6000`, experiment)
  
anime.b.ichart %<>% 
  mutate(experiment = "e1") %>% 
  select(Sub.Num, Tr.Num, Months, Prescreen.Notes, Target.Image,
         Condition, Response, RT, `0`:`6000`, experiment)

anime.c.ichart %<>%  
  mutate(experiment = "e2") %>% 
  select(Sub.Num, Tr.Num, Months, Prescreen.Notes, Target.Image,
         Condition, Response, RT, `0`:`6000`, experiment)
```

Merge iCharts for analysis.

```{r merge iCharts}
ichart.analysis <- bind_rows(anime.a.ichart, anime.b.ichart, anime.c.ichart)
```

Clean up target.image variable, so we can model item as a random effect. 

```{r}
targets <- c("horse", "sheep", "cow", "dog", "tapir", "aardvark", "capybara", "pangolin")

make_clean_target <- function (target_image, targets) {
  target_img_clean <- targets[str_detect(target_image, targets)]
  return(target_img_clean)
}

ichart.analysis$clean_target_img <- unlist(sapply(ichart.analysis$Target.Image, 
                                         function (x) make_clean_target(x, targets)))
```

### Compute statistics

```{r}
# define onset and reject prescreen
ichart.analysis <- defineOnset(ichart.analysis[ichart.analysis$Prescreen.Notes == "",], 
                               critonset=0, includeAways=TRUE)

# compute RT and gaps
ichart.analysis <- computeStatistics(ichart.analysis, startWindow=0, endWindow=2500)

# reject trials with extreme RT and gaps
ichart.analysis <- filteriChart(ichart.analysis, minRT=0, maxRT=2200, maxfirstgap=15, maxlonggap=15)
```

### Convert iChart to long format 

```{r}
ichart.analysis.long <- ichart.analysis %>% 
  gather(key = Time.ms, value = value, `0`:`6000`) %>% 
  filter(value %in% c("0", "1", "0.5", ".", "-")) %>%
  mutate(value = ifelse(value == "-", ".", value),
         value_cat = factor(value, labels = c("Away", "Distractor", "Target")),
         Time.ms_numeric = to.n(Time.ms))
```

Merge CDI data.

```{r cdi merge}
cdi_df <- bind_rows(anime_cdi, animoo_cdi) %>% 
  dplyr::rename(Sub.Num = ParticipantId) %>% 
  filter(duplicated(Sub.Num) == FALSE) # REMOVES ANY DUPLICATES
```

Spread out the condition information, so we only have one piece of information stored in each column.

```{r}
ichart.analysis.long %<>% 
  separate(col = Condition, into = c("cue_type", "target_img_type", 
                                     "distracter_img_type", "trial_type"))
```

### Write tidy data

```{r write data}
write_csv(ichart.analysis.long, "../../data/02_tidy_data/anime_tidy_ichart.csv")
write_csv(cdi_df, "../../data/02_tidy_data/anime_tidy_cdi.csv")
```
